Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-11 inc/conclusions.tex
finished major work on conclusions

The desire to reduce the transverse momentum uncertainty $\Delta p_{\smallT}$ --- in an effort to reduce the rms transverse emittance $\varepsilon_{\smallT}$ and thereby improve the resolving power of the electron pulse~\cite{berger_dc_2009} --- has driven us to explore many photocathodes and even several different photoemission processes.

>>>>

The desire to reduce the transverse momentum uncertainty $\Delta p_{\smallT}$ --- in an effort to reduce the rms transverse emittance $\varepsilon_{\smallT}$ and thereby improve the resolving power of the electron pulse~\cite{berger_dc_2009} --- has driven us to explore many photocathodes and even several different photoemission processes.
I have demonstrated that single photon photoemission and two-photon thermionic photoemission were not likely candidates to reduce the $\Delta p_{\smallT}$ as those processes were tied to intrinsic properties of the material which couldn't provide high-yield and low emittance simultaneously.
Recently, however, we have discovered that for those processes, the effective electron mass $m^*$ should have been considered, and therefore we are currently revisiting many of the materials that fall into these categories, a publication on this topic is in preparation.

I have also presented our efforts to employ periodic nanostructured photocathode surfaces, designed to allow the incident laser to drive a surface plasmon, in hopes that a surface plasmon field might reduce the transverse emittance \cite{zawadzka_evanescent_2001,kupersztych_ponderomotive_2001,kupersztych_anomalous_2005,li_surface_2013}.
Though we had success in driving the plasmon, we were unable to demonstrate reduction in $\Delta p_{\smallT}$.
We believe the problems were due to disturbances in the acceleration field near these nanostructures, though efforts to mitigate those disturbances has yet been unsuccessful.

Our most promising results have come from excited-state thermionic emission (ESTE) sources, GaSb and InSb.
In this process the laser promotes carriers from the valence band to an upper conduction band close to the vacuum level, reducing the effective work function.
The electron temperature, elevated by the laser, causes the tail of the Fermi distribution to exceed the effective work function and thus emission occurs.
Importantly, the results we observed were inconsistent with predictions until we considered the effective mass of these upper conduction bands.
Not only did this allow our prediction to match the experimental results, it opened our eyes to the possibilities of low effective mass materials, even for photoemission processes other than ESTE.
As I have mentioned earlier, this work is ongoing and is a very exciting avenue for future research.
